---
title: "AT4BR_Exercise_7_Kinga_Zajdel_2024-04-17"
author: "Kinga Zajdel"
format: html:
      embed-resources: true
      theme: hpstr
      toc: true
      toc-color: violet
      toc-location: left
      toc-depth: 6
      toc-expand: 6
      code-tools:
        source: true
        toggle: true
      code-fold: false
      code-summary: "Show the code"
      code-overflow: wrap
      page-layout: full
---

## mending the figure

#### about the data

On the page: <https://www.statista.com/statistics/1246890/vehicles-use-united-states-historical/> I have found information that in 80's in the US there were around 120.000-140.000 vehicles registered. For the purposes of the task, I assume that there were equal numbers of Chevy, Ford, Toyota, and Nissan/Datsun. As we are not talking about number of cars being used that time but **percentage of cars bought through previous ten years and still working**, the exact numbers play smaller role here.
Also, the percentage is rounded because in my source there were no precise numbers.

```{r}
# installing the packages

# use ggplot2
# library(ggplot2)

# color-blind friendly palette
# install.packages("viridis")
# library(viridis)

```
```{r}
# setting size of groups
how_many_Chevy <- 30000
how_many_Ford <- 30000
how_many_Toyota <- 30000
how_many_Nissan_Datsun <- 30000

# setting percentage of still working cars according to the ad
percent_Chevy <- 0.983
percent_Ford <- 0.975
percent_Toyota <- 0.965
percent_Nissan_Datsun <- 0.953

# numbers for the data frame
# cars_dataset <- c(
#   how_many_Chevy * percent_Chevy,
#   how_many_Ford * percent_Ford,
#   how_many_Toyota * percent_Toyota,
#   how_many_Nissan_Datsun * percent_Nissan_Datsun)
cars_dataset <- c(
  percent_Chevy,
  percent_Ford,
  percent_Toyota,
  percent_Nissan_Datsun)

# names for the data frame
cars_names <- c("Chevy", "Ford", "Toyota", "Nissan_Datsun")

# preparing the dataset for the plot
cars_ad_data<- data.frame(cars_names, cars_dataset) 
cars_ad_data 

```

How the plot should look like

```{r}
 ggplot(data = cars_ad_data, aes(x=cars_names))+
  geom_bar(aes(y=cars_dataset),stat = "summary", fun = "mean")+
  scale_fill_viridis_d() + scale_x_discrete(limits = cars_names)
```



```{r}
ggplot(data.frame(x = cars_names, y = cars_dataset), aes(x = x, y = y)) +
  coord_fixed() +
  scale_fill_viridis() + theme_bw()

```

```{r}
ggplot(data=cars_ad_data, aes(x=cars_dataset, y=cars_dataset)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=cars_dataset), vjust=-0.3, size=3.5)+
  theme_minimal()

```

*No AI used.*
